---
title: "Love vs extraterrestials"
author: "Jose Torres Vargas"
date: "Spring 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
help("m111surveyfa13")
mydata<-m111surveyfa13 <- na.omit(m111surveyfa13)
```

# A question of Belief

Your data is in the dataframe called "mydata" examine it in the environment tab  
do a variable analysis on the 3 Questions and then upload the appropriate Rmd template for this job.   
Also create an empty github repository called "Belief" and make it the remote repository for  
this assignment.  For each question supply graphical evidence, numerical summaries, an inferential test, and a conclusion.  When finished push your rmd file, your project file, and your knitted html file to your github repo.  Finally turn in to Canvas the link to your github repo.




# Your First Question  

### Do people who believe in Love at First sight also tend to believe in Life on other planets?
Graphical display
```{r}
barchartGC(~love_first + extra_life,data=mydata, xlab = "love @ first sight")
```
People that believe in love in first sight, also tend to belive in ET?
$H_O$: there is no relation between belief in first sight, and belief in ET.
$H_A$: There is a belive in love and first sight and ET.  

Numerical Summary
```{r}
table1 <- xtabs(~love_first + extra_life, mydata)
rowPerc(table1)
colPerc(table1)

```
Inference
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

P> .05 --> REJECT HO
  
    
# Your second Question  

### Is there a difference between boys and girls with respect to belief in life on other planets?
Graphical Display
```{r}
barchartGC(~extra_life + sex,data=mydata, xlab = "Extra life")
```
$N_O$ There is no difference between sex and the believe of extra life in other planets.

Numerical summary
```{r}
table1 <- xtabs(~extra_life + sex, data=mydata,)
rowPerc(table1)
colPerc(table1)
```
Inference
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
P> .05 –> REJECT HO
 
# Your last Question   


### Is there a difference between boys and girls with respect to belief in love at First sight?

Graphical Display

```{r}
barchartGC(~sex + love_first ,mydata, xlab = "sex")
```
Graph illustration of sex vs belief in love at first sight

$H_O$ There is no difference between boys and girls in belief of love in first sight

Numerical
```{r}
table1 <- xtabs(~sex + love_first, data=mydata)
rowPerc(table1)
colPerc(table1)
```


Inference
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
P> .05 –> REJECT HO

